### 2012-06-05 docs/getting_started/getting_started.tex
update for recent directory changes

This option specifies the Fortran compiler.  We will use {\tt
gfortran}, which is the preferred compiler for \maestro.  Specifying
this compiler will automatically pull in the compiler settings as
specified in {\tt BOXLIB\_HOME/Tools/F\_mk/}.  (Alternate compiler
choices include {\tt Intel}, {\tt PGI}, {\tt PathScale}.)

@@

\amrvis\ uses the {\tt Motif} library for defining the GUI.  On a Linux 
system, you may need to install the {\tt lesstif} package and any
related development packages (e.g.\ {\tt lesstif-devel}).  Depending
on your Linux system, you may also need to install {\tt libXpm} and
related development packages (e.g.\ {\tt libXpm-devel}).  Also, in
{\tt BoxLib/Tools/C\_mk/Make.defs}, the Fortran libraries are
explictly linked in by asking {\tt gfortran} for the location of {\tt
libgfortran.a}.  You may need to explicitly install the static
libraries for {\tt gfortran} (i.e.\ {\tt libgfortran-static}), or
change the library line to query for the shared-object version {\tt
libgfortran.so}.

@@

By default, \maestro\ outputs global diagnostics each timestep into a
file called {\tt maestro\_diag.out}.  This includes the maximum Mach
number, peak temperature, and peak nuclear energy generation rate.
Individual problems can provide their own {\tt diag.f90} file to
produce custom diagnostic output.  This information can be plotted
directly with {\sl GNUplot}, for example.

@@

Different problems in \maestro\ are contained in one of three
sub-directories under {\tt MAESTRO/} ({\tt SCIENCE/}, {\tt
TEST\_PROBLEMS}, or {\tt UNIT\_TESTS}).  The {\tt GNUmakefile} in each
problem directory lists the components of {\tt MAESTRO} that are used
to build the executable.  {\tt TEST\_PROBLEMS/} contains simple
problems that were used in the development of \maestro.  Many
of these were featured in the papers describing the \maestro\ algorithm.

@@

{\tt spherical\_heat} maps a spherical star (a Chandrasekhar-mass white
dwarf) onto the Cartesian domain and uses an external heat source to
cause the star to expand.  This is the 3D analogue of the {\tt
  test\_basestate} unit test (see \S~\ref{sec:unit_tests}).  This
problem was discussed in \cite{multilevel}.

@@

>>>>

This option specifies the Fortran compiler.  We will use {\tt
gfortran}, which is the preferred compiler for \maestro.  Specifying
this compiler will automatically pull in the compiler settings as
specified in {\tt BOXLIB\_HOME/Tools/F\_mk/}.  (Alternate compiler
choices include {\tt Intel}, {\tt PGI}, {\tt PathScale}, {\tt Cray}.)

@@

\amrvis\ uses the {\tt Motif} library for defining the GUI.  On a Linux 
system, you may need to install the {\tt lesstif} package and any
related development packages (e.g.\ {\tt lesstif-devel}).  Depending
on your Linux system, you may also need to install {\tt libXpm} and
related development packages (e.g.\ {\tt libXpm-devel}).

@@

By default, \maestro\ outputs global diagnostics each timestep into a
file called {\tt maestro\_diag.out}.  This includes the maximum Mach
number, peak temperature, and peak nuclear energy generation rate.
Individual problems can provide their own {\tt diag.f90} file to
produce custom diagnostic output.  This information can be plotted
directly with {\sf GNUplot}, for example.

@@

Different problems in \maestro\ are contained in one of three
sub-directories under {\tt MAESTRO/} ({\tt SCIENCE/}, {\tt
TEST\_PROBLEMS/}, or {\tt UNIT\_TESTS/}).  The {\tt GNUmakefile} in each
problem directory lists the components of {\tt MAESTRO} that are used
to build the executable.  {\tt TEST\_PROBLEMS/} contains simple
problems that were used in the development of \maestro.  Many
of these were featured in the papers describing the \maestro\ algorithm.

@@

{\tt spherical\_heat} maps a spherical star (a Chandrasekhar-mass white
dwarf) onto the Cartesian domain and uses an external heat source to
cause the star to expand.  This is the 3D analogue of the {\tt
  test\_basestate} unit test (see \S~\ref{chapter:unit_tests}).  This
problem was discussed in \cite{multilevel}.

@@

\section{Parallel Jobs}

To run in parallel with MPI, you would set {\tt MPI := t} in your {\tt
GNUmakefile}.  For a machine with working MPI compiler wrappers ({\tt
mpif90} and {\tt mpicc}), setting the environment variable {\tt
BOXLIB\_USE\_MPI\_WRAPPERS=1} will have the code build using these
wrappers.  This is the easiest way to do a parallel build, and should
work on most Linux systems.

More generally, the build system needs to know about your MPI
installation.  For popular national computing facilities, this is
already setup, and the build system looks at the machine hostname to
set the proper libraries.  For other machines, you may need to edit
the {\tt GMake.MPI} file in the \boxlib\ build files.  See
\S~\ref{ch:make} for more details.

OpenMP can be used to parallelize on shared-memory machines (i.e.\
within a node).  OpenMP support is accomplished through the compiler.
Setting {\tt OMP := t} in the {\tt GNUmakefile} will enable the proper
compiler flags to build with OpenMP.  Note: not all \maestro\ modules 
have OpenMP support.  Microphysics routines need to be written in a
threadsafe manner.  This can be tested via the {\tt test\_react} unit
test (see ~\S~\ref{chapter:unit_tests}).

### 2012-06-05 docs/preface/preface.tex
boxlib
minor tweak
update for recent directory changes

>>>>

\noindent \maestro\ uses the \boxlib\ library,
developed at the Center for Computational Sciences and
Engineering at Lawrence Berkeley National Laboratory.  \boxlib\
is distributed separately from \maestro\ (see https:/\hspace{-0.25em}/ccse.lbl.gov/BoxLib/ )
\\

\noindent The {\tt helmeos} equation of state was developed by Frank Timmes (ASU).
The version in \maestro\ was downloaded from his website and the
interface changes slightly for threadsafeness.  We thank Frank for
making it available.
